Model Samples Processing

### 2020-02-20 stats/model_comparison.Rmd
add model comparison
add dev mixture model

>>>>

# Model comparison explanation

model_like <- bind_rows(

  readRDS("../saves/model_pred_prag_fb.rds") %>%
    mutate(model = "fullBayes")%>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k)

    ,readRDS("../saves/model_pred_mm.rds") %>%
    mutate(model = "mixture")%>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k)

      ,readRDS("../saves/model_pred_dmm.rds") %>%
    mutate(model = "dev_mixture")%>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k)
) %>%
  mutate(
    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
  ) %>%
  group_by(chain, model, iteration) %>%
  summarize(total_likelihood_sample = sum(log_like))

# variation across chains

model_by_chain <- model_like %>%
  na.omit(chain)%>%
  group_by(model, chain) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)

saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain.rds")

# compare models
model_comp <- model_like %>%
  na.omit(chain)%>%
  group_by(model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)%>%
  mutate(fb_vs_free = fullBayes - pragmatic,
          fb_vs_mixture= fullBayes - mixture,
         fb_vs_dev_mixture= fullBayes - dev_mixture,
          free_vs_mixture = pragmatic - mixture,
         free_vs_dev_mixture = pragmatic - dev_mixture,
         dev_mixture_vs_mixture = dev_mixture - mixture
         ) %>%
  select(-pragmatic, -fullBayes, -mixture, -dev_mixture) %>%
  gather(model, logBF)

saveRDS(model_comp, "../saves/expl_model_comparison.rds")

### 2020-02-20 stats/model_sample_processing.Rmd
add dev mixture model

>>>>

# developmental mixture model

model <- bind_rows(
 fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain1.csv",header = T)%>%mutate(chain = 1),
 fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain2.csv",header = T)%>%mutate(chain = 2),
  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain3.csv",header = T)%>%mutate(chain = 3),
  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
  fread("../webppl/output/samples-fullBayes-devMixtureModel-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
)

saveRDS(item_params, "../saves/item_params_dmm.rds")

saveRDS(global_params, "../saves/global_params_dmm.rds")

saveRDS(item_sigma, "../saves/item_sigma_dmm.rds")

mixture<- model %>%
  filter(b == "mixtureComponent")%>%
  select(b,c,g,chain)%>%
    rename(parameter = b,
           type = c,
         value = g)

saveRDS(mixture, "../saves/mixture_dmm.rds")

model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "devMixtureModel")%>%
  select(-a, -h, -c)%>%
  rename(model = b, 
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prag, "../saves/model_pred_dmm.rds")
